### 2022-01-13 cv/cv-body.tex
Update some pubs

@@

@@

marine warming are worse in already warmer temperate waters. In press at
Fish and Fisheries. \url{https://doi.org/10.1111/faf.12613}. Open access
preprint: \url{https://doi.org/10.32942/osf.io/b87ng}.

@@

decades. In press at Frontiers in Ecology and the Environment.

@@

of species distribution change by incorporating local trends. In press
at Ecography. \url{https://doi.org/10.1111/ecog.05176}.

@@

control measures using a Bayesian model of physical distancing. In press
at PLOS Computational Biology:

@@

bottom trawl data. In press at Global Change Biology.

@@

\begin{description}
\tightlist
\item[2020]
Haggarty D.R., Q.C. Huynh, R.E. Forrest, \textbf{S.C. Anderson}, M.J.
Bresch, E.A. Keppel. Evaluation of potential rebuilding strategies for
Inside Yelloweye Rockﬁsh (\emph{Sebastes ruberrimus}) in British
Columbia. Accepted as a DFO Can. Sci. Advis. Sec. Res. Doc. on June 11
2020.
(\href{https://www.dropbox.com/s/pll8axzsxqka8j8/resdoc-iye.pdf?dl=1}{English
version}).
\item[2020]
\textbf{Anderson, S.C.}, R.E. Forrest, Q.C. Huynh, E.A. Keppel. A
management procedure framework for groundﬁsh in British Columbia.
Accepted as a DFO Can. Sci. Advis. Sec. Res. Doc. on June 9 2020.
(\href{https://www.dropbox.com/s/rgxk2wco5v5zp0e/gfmp-2020-03-13.pdf?dl=1}{English
version}).
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/SAR-AS/2021/2021_002-eng.html}{Associated
Science Advisory Report}.
\item[2020]
Forrest, R.E., \textbf{S.C. Anderson}, C.J. Grandin, P.J. Starr.
Assessment of Pacific Cod (\emph{Gadus macrocephalus}) for Hecate Strait
and Queen Charlotte Sound (Area 5ABCD), and West Coast Vancouver Island
(Area 3CD) in 2018. DFO Can. Sci. Advis. Sec. Res. Doc. 2020/070 iv +
204 p.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-fra.html}{French
version}).
\item[2019]
\textbf{Anderson, S.C.}, E.A. Keppel, A.M. Edwards, 2019. A reproducible
data synopsis for over 100 species of British Columbia groundfish. DFO
Can. Sci. Advis. Sec. Res. Doc. 2019/041. vii + 321 p.
(\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-eng.html}{English
version},
\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-fra.html}{French
version}).
\end{description}

@@

\begin{description}
\tightlist
\item[2019]
\textbf{Anderson, S.C.}, and Workman, G.D. A review of groundfish
surveys in 2018 and an introduction to the groundfish data synopsis
report. In State of the physical, biological and selected fishery
resources of Pacific Canadian marine ecosystems in 2018. Edited by J.L.
Boldt, J. Leonard, and P.C. Chandler. pp. 90--94. Can. Tech. Rep.\ Fish.
Aquat. Sci. 3314, Sidney, BC.
(\href{https://www.dfo-mpo.gc.ca/oceans/publications/soto-rceo/2018/index-eng.html}{English
version})
\item[2020]
English, P.A., \textbf{Anderson, S.C.}, and Workman, G.D. A review of
groundfish surveys in 2019. In State of the physical, biological and
selected fishery resources of Pacific Canadian Marine Ecosystems in
2019. Edited by J.L. Boldt, A. Javorski, and P.C. Chandler.
pp.\ 102--106. Can. Tech. Rep.\ Fish. Aquat. Sci. 3377, Sidney, BC.
(\href{https://www.dfo-mpo.gc.ca/oceans/publications/soto-rceo/2019/index-eng.html}{English
version})
\item[2018]
Edwards, A.M., Duplisea, D.E., Grinnell, M.H., \textbf{Anderson, S.C.},
Grandin, C.J., Ricard, D., Keppel, E.A., Anderson, E.D., Baker, K.D.,
Benoit, H.P., Cleary, J.S., Connors, B.M., Desgagnes, M., English, P.A.,
Fishman, D.F., Freshwater, C., Hedges, K.J., Holt, C.A., Holt, K.R.,
Kronlund, R., Mariscak, A., Obradovich, S.G., Patten, B.A., Rogers, B.,
Rooper, C.N., Simpson, M.R., Surette, T.J., Tallman, R.F., Wheeland,
L.J., Wor, C., and Zhu, X. 2018. Proceedings of the Technical Expertise
in Stock Assessment (TESA) national workshop on ``Tools for transparent,
traceable, and transferable assessments'' 27--30 November 2018 in
Nanaimo, British Columbia. Can. Tech. Rep.\ Fish. Aquat. Sci. 3290,
Nanaimo, BC.
(\href{https://waves-vagues.dfo-mpo.gc.ca/Library/40750152.pdf}{English
version})
\end{description}

>>>>

\hypertarget{preprints}{%
\section{Preprints}\label{preprints}}

\begin{description}
\tightlist
\item[2021]
\textbf{Anderson, S.C}, B.M. Connors, P.A. English, R.E. Forrest, R.
Haigh, K.R. Holt. Trends in Pacific Canadian groundfish stock status.
bioRxiv 2021.12.13.472502.
\url{https://doi.org/10.1101/2021.12.13.472502}.
\end{description}

@@

\item[2022]
Stockdale, J.E., \textbf{S.C. Anderson}, A.M Edwards, S.A. Iyaniwura, N.
Mulberry, M.C. Otterstatter, N.Z. Janjua, D. Coombs, C. Colijn, and
M.A.\ Irvine. Quantifying transmissibility of SARS-CoV-2 and impact of
intervention within long-term healthcare facilities. Royal Society Open
Science 9(1): 211710. \url{https://doi.org/10.1098/rsos.211710}.
\item[2022]
Commander C.J.C, L.A.K. Barnett, E.J. Ward, \textbf{S.C. Anderson}, T.E.
Essington. The shadow model: how and why small choices in spatially
explicit species distribution models affect prediction. In press at
PeerJ.
\item[2022]
Ward, E.J., \textbf{S.C. Anderson}, M.D.\ Hunsicker, and M.A.\ Litzow.
Smoothed dynamic factor analysis for identifying trends in multivariate
time series. Methods in Ecology and Evolution. In press.
\url{https://doi.org/10.1111/2041-210X.13788}.

@@

marine warming are worse in already warmer temperate waters. Fish and
Fisheries. 23(1) 239--255. \url{https://doi.org/10.1111/faf.12613}. Open
access preprint: \url{https://doi.org/10.32942/osf.io/b87ng}.

@@

decades. Frontiers in Ecology and the Environment. 19(5): 274--282.

@@

of species distribution change by incorporating local trends. Ecography.
44: 427--439. \url{https://doi.org/10.1111/ecog.05176}.

@@

control measures using a Bayesian model of physical distancing. PLOS
Computational Biology. 16(12): e1008274.

@@

bottom trawl data. Global Change Biology. 27: 220--236.

@@

\begin{description}
\tightlist
\item[2021]
\textbf{Anderson, S.C.}, R.E. Forrest, Q.C. Huynh, E.A. Keppel. A
management procedure framework for groundﬁsh in British Columbia. DFO
Can. Sci. Advis. Sec. Res. Doc. 2021/007.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_007-eng.html}{Research
Document}).
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/SAR-AS/2021/2021_002-eng.html}{Associated
Science Advisory Report}.
\item[2020]
Haggarty D.R., Q.C. Huynh, R.E. Forrest, \textbf{S.C. Anderson}, M.J.
Bresch, E.A. Keppel. Evaluation of potential rebuilding strategies for
Inside Yelloweye Rockﬁsh (\emph{Sebastes ruberrimus}) in British
Columbia. Accepted as a DFO Can. Sci. Advis. Sec. Res. Doc. on June 11
2020.
(\href{https://www.dropbox.com/s/pll8axzsxqka8j8/resdoc-iye.pdf?dl=1}{English
version}).
\item[2020]
Forrest, R.E., \textbf{S.C. Anderson}, C.J. Grandin, P.J. Starr.
Assessment of Pacific Cod (\emph{Gadus macrocephalus}) for Hecate Strait
and Queen Charlotte Sound (Area 5ABCD), and West Coast Vancouver Island
(Area 3CD) in 2018. DFO Can. Sci. Advis. Sec. Res. Doc. 2020/070 iv +
204 p.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-fra.html}{French
version}).
\item[2019]
\textbf{Anderson, S.C.}, E.A. Keppel, A.M. Edwards, 2019. A reproducible
data synopsis for over 100 species of British Columbia groundfish. DFO
Can. Sci. Advis. Sec. Res. Doc. 2019/041. vii + 321 p.
(\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-eng.html}{English
version},
\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-fra.html}{French
version}).
\end{description}

@@

\begin{description}
\tightlist
\item[2020]
English, P.A., \textbf{Anderson, S.C.}, and Workman, G.D. A review of
groundfish surveys in 2019. In State of the physical, biological and
selected fishery resources of Pacific Canadian Marine Ecosystems in
2019. Edited by J.L. Boldt, A. Javorski, and P.C. Chandler.
pp.\ 102--106. Can. Tech. Rep.\ Fish. Aquat. Sci. 3377, Sidney, BC.
(\href{https://www.dfo-mpo.gc.ca/oceans/publications/soto-rceo/2019/index-eng.html}{English
version})
\item[2019]
\textbf{Anderson, S.C.}, and Workman, G.D. A review of groundfish
surveys in 2018 and an introduction to the groundfish data synopsis
report. In State of the physical, biological and selected fishery
resources of Pacific Canadian marine ecosystems in 2018. Edited by J.L.
Boldt, J. Leonard, and P.C. Chandler. pp. 90--94. Can. Tech. Rep.\ Fish.
Aquat. Sci. 3314, Sidney, BC.
(\href{https://www.dfo-mpo.gc.ca/oceans/publications/soto-rceo/2018/index-eng.html}{English
version})
\item[2018]
Edwards, A.M., Duplisea, D.E., Grinnell, M.H., \textbf{Anderson, S.C.},
Grandin, C.J., Ricard, D., Keppel, E.A., Anderson, E.D., Baker, K.D.,
Benoit, H.P., Cleary, J.S., Connors, B.M., Desgagnes, M., English, P.A.,
Fishman, D.F., Freshwater, C., Hedges, K.J., Holt, C.A., Holt, K.R.,
Kronlund, R., Mariscak, A., Obradovich, S.G., Patten, B.A., Rogers, B.,
Rooper, C.N., Simpson, M.R., Surette, T.J., Tallman, R.F., Wheeland,
L.J., Wor, C., and Zhu, X. 2018. Proceedings of the Technical Expertise
in Stock Assessment (TESA) national workshop on ``Tools for transparent,
traceable, and transferable assessments'' 27--30 November 2018 in
Nanaimo, British Columbia. Can. Tech. Rep.\ Fish. Aquat. Sci. 3290,
Nanaimo, BC.
(\href{https://waves-vagues.dfo-mpo.gc.ca/Library/40750152.pdf}{English
version})
\end{description}
